### 2017-06-18 paper.tex
Small latex formatting fixes

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Univ Lyon, UJM-Saint-Etienne, F-42023, France / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com \\

@@

Thinking systematically about difficulty levels can help manage expectations.
For example,
Programming Historian project labels lessons ``beginner'',
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
This method works, however, only if there is prior agreement on what those terms mean.

@@

Lessons don't maintain themselves.
For technical lessons, software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case, what was cutting edge in 2017 may be dated
and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

@@

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contributions.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
Lesson releases should use a consistent naming scheme,
such as the full year and month of the release,
e.g. ``2017.05''.
This is the scheme Software Carpentry has used in
its releases of its lessons \cite{shell2015,shell2017}.

@@

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and the Carpentry projects
use the Creative Commons - Attribution license
(\url{https://creativecommons.org/licenses/by/4.0/}),
which allows people to share and adapt material for any purpose
as long as they cite the original source.

@@

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that they have the usual keywords in their bibliographic entries
and HTML page headers.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Universit\'{e} Jean Monnet / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com \\

@@

Thinking systematically about difficulty levels can help manage expectations.
For example,
Programming Historian project labels lessons ``beginner,''
``intermediate,''
and ``advanced''
to help authors write at appropriate levels.
This method works, however, only if there is prior agreement on what those terms mean.

@@

Lessons don't maintain themselves.
For technical lessons software versions and dependencies are constantly changing,
while for more traditional academic lessons the literature is advancing at an ever increasing pace.
In either case, what was cutting edge in 2017 may be dated
and less useful in 2018.
This needs to be clear to contributors,
so they understand that this lesson is just
the starting point.
Sustainability needs to be front of mind.

@@

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contributions.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
Lesson releases should use a consistent naming scheme,
such as the full year and month of the release,
e.g. ``2017.05.''
This is the scheme Software Carpentry has used in
its releases of its lessons \cite{shell2015,shell2017}.

@@

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and the Carpentry projects
use the Creative Commons -- Attribution license
(\url{https://creativecommons.org/licenses/by/4.0/}),
which allows people to share and adapt material for any purpose
as long as they cite the original source.

@@

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that have the usual keywords in their bibliographic entries
and HTML page headers.
